\newpage
\begin{center}
    {\large \textbf{Olivaris - Plataforma de gestión colaborativa para el olivar}}

    \vspace{0.2cm}
    {\normalsize Jorge Cano Melero}

    \vspace{0.2cm}
\end{center}

\vspace{0.5cm}

\textbf{Keywords:} Commercial Farm Logbook, Agricultural Management, Backend, REST API, JWT, SIGPAC, Parcels, Phytosanitary Treatments.

\vspace{0.5cm}

\textbf{Abstract:}

This Final Degree Project addresses the design and implementation of Olivaris, a collaborative management platform aimed at farmers and authorised entities to centralise the registration and tracking of information related to the olive grove. The project arises from the need to replace manual and scattered working methods with a digital solution capable of organising parcels, plots, activities and the documentation associated with the farm in a more efficient way, thereby improving traceability and supporting compliance with future regulatory requirements.

The proposed solution is built on a client-server architecture, with a backend responsible for exposing a REST API for the management of users, parcels and activities, and a frontend designed to provide a clear and intuitive user experience. The system includes authentication and access control mechanisms based on JWT and role permissions, ensuring that each user can access only the information and functionality corresponding to their role. Special attention has also been given to the spatial representation of parcels and plots, as well as to the handling of phytosanitary activities.

In addition, the platform has been designed with extensibility in mind, so that it can serve as a foundation for future integrations with external services related to agricultural management. In this context, the work is not limited to implementing a functional application, but also defines a technological structure that promotes maintainability, system evolution and adaptation to new requirements.

Ultimately, Olivaris provides a digital tool that helps modernise olive grove management, moving towards a more efficient, centralised and accessible agricultural administration.